\documentclass[ComputerScience]{vita}

\addtolength{\textwidth}{2in}
\addtolength{\oddsidemargin}{-1in}
\addtolength{\evensidemargin}{-1in}
\setlength{\topsep}{-0.7in}
\setlength{\parskip}{0in}
\topmargin=0in
\textheight=10.1in
% make "C++" look pretty when used in text by touching up the plus signs
\newcommand{\CPP}
{C\nolinebreak[4]\hspace{-.05em}\raisebox{.60ex}{\tiny\bf ++}}

\newenvironment{suber}[0]
{\begin{list}{$\bullet$}
	{\setlength{\topsep}{-0.4in}
		\setlength{\leftmargin}{0.25in}
		\setlength{\itemsep}{0.01in}}
}
{\end{list}\par}

\newenvironment{suberb}[0]
{\begin{list}{$\circ$}
	{\setlength{\topsep}{-0.4in}
		\setlength{\leftmargin}{0.25in}
		\setlength{\itemsep}{0.01in}}
}
{\end{list}\par}

\begin{document}
\topmargin=-1in
\name{{\bf Douglas Rapp} \\ douglas.rapp@gmail.com, (415) 637-0538\\ 1677 Bush St. Apt. 21, San Francisco, CA 94109\\[15pt]}                             
\title{}
\begin{vita}
\quad\\
{\bf {\large Objective}}\ \hrulefill
\begin{list}{}{\setlength{\leftmargin}{.25in}}
\item I like solving hard problems and building big scalable systems.
\end{list}
{\bf{\large Experience}}\ \hrulefill
\begin{list}{}{\setlength{\leftmargin}{.25in}}
    \item {\bf Layer (2014-2018)}\\
    {\em Senior Software Engineer, Platform Lead (San Francisco, CA)}
    \begin{suber}
	\item Built a world-class messaging system for mobile and web from the ground up
		\begin{suberb}
			\item Worked full stack from Android devices, to Erlang and Scala services, to CoreOS and Kubernetes.
		\end{suberb}
    \item Led a team of five to develop and maintain the Layer messaging backend service.
		\begin{suberb}
			\item Wrote product and engineering specs for new features.
            \item Worked with newer engineers to get features implemented.
            \item Coordinated with the client and infrastructure teams.
		\end{suberb}
    \item Designed and implemented the Layer REST APIs
        \begin{suberb}
            \item Built Scala server backed by nginx and rabbitmq that can serve partitioned users.
            \item Used postgres as a cache and materialized view to get data ready for REST access.
            \item Adapated a mobile sync protocol to reconcile data from Cassandra.
        \end{suberb}
    \item Implemented the Layer authentication protocol on the server in Erlang
		\begin{suberb}
			\item Built a rest endpoint in that handles CSR requests to generate client certificates
            \item Implemented a JWT-based scheme for doing federated user auth
		\end{suberb}
    \item Built a push server to notify about messages over APNs and GCS
        \begin{suberb}
            \item Worked in Erlang to maintain persistent connections and route user messages
        \end{suberb}
    \item Built a badging system to add unread count to push notifications for mobile devices.
    \item Built a ``Rich Content'' system for mobile clients to attach large files to messages
		\begin{suberb}
            \item Added APIs to generate authorized upload and download urls for Google Cloud Storage
            \item Implemented async resumable upload and download on Android
		\end{suberb}
    \item Laid out the foundations for using Erlang and Cassandra in the core messaging server
    \item Foundational work on the Android SDK transport and persistence layers.
    \item Built out a jenkins/nexus infrastructure for build and dependency management.
    \end{suber}
    \item {\bf StackMob (2012-2014)}\\
    {\em Software Engineer (San Francisco, CA)}
    \begin{suber}
    \item Worked on a massively scalable Mobile Backend as a Service providing
        datastore APIs, push notifications, and custom code solutions for
        mobile apps
	\item Rewrote the push server for scalability and performance using Riak, and added GCM support.
	\item Evolved and owned the Java/Android SDKs, adding an ORM and upsert API
	\item Implemented rich OAuth2 permission options for the datastore and dynamic per-app CORS
    \end{suber}
    \item {\bf Adobe AIR Team (2008-2011) and Flash Runtime Mobile Team (2011-2012)}\\
    {\em Software Engineer (San Francisco, CA)}
    \begin{suber}
	\item Implemented features and fixed over 1,000 bugs in areas including rendering, video, and OS interaction 
	\item Developed across  Android, iOS, Windows, and Mac on a huge, multi-language, legacy codebase
    \end{suber}
\end{list}
{\bf{\large Technical Skills}}\ \hrulefill
\begin{list}{}{\setlength{\leftmargin}{.25in}}
	\item {\bf Core Languages:} Scala, Erlang, Java
	\item {\bf Familiar Languages:} C, \CPP, Python, \LaTeX{}, 
	\item {\bf Technologies:} Cassandra, Postgresql, Kubernetes, RabbitMQ, Akka
\end{list}
{\bf {\large Education}}\ \hrulefill
\begin{list}{}{\setlength{\leftmargin}{.25in}}
\item {\bf Brown University,
	B.S. in Mathematics/Computer Science (2004-2008)}\\
	{\em Coursework in Algorithms, Computer Graphics, and Machine Learning }
\end{list}
\end{vita}
\end{document}
